---
title: "boxknapsack"
author: "Boxi Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The boxknapsack package contains three different algorithm to solve the knapsack problem:
  - brute force
- dynamic programming 
- greedy approach

The data we will use is generated in the following way:
  
```{r}
set.seed(42)
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )

library(boxknapsack)
```



**Brute force search**

__Question__ How much time does it takes to run the algorithm for n = 16 objects?

__Question__ What performance gain could you get by parallelizing brute force search?
```{r}
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500)
st <- system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500))
st
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500, parallel = TRUE)
st <- system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500, parallel = TRUE))
st

```
The time is measured by system.time(). By using parallelizing brute force, the user time is saved around 24 fold.



__Question__ How much time does it takes to run the algorithm for n = 500 objects?
**Dynamic programming**
```{r}
knapsack_dynamic(x = knapsack_objects[1:16,], W = 2000)
system.time(knapsack_dynamic(x = knapsack_objects[1:16,], W = 2000))

knapsack_dynamic(x = knapsack_objects[1:500,], W = 2000)
system.time(knapsack_dynamic(x = knapsack_objects[1:16,], W = 2000))
```
When n = 500, it seems the time uesd is even less.


__Question__ How much time does it takes to run the algorithm for n = 1000000 objects?
**Greedy heuristic**
```{r}
set.seed(42)
n <- 1000000
knapsack_objects <-
 data.frame(
   w=sample(1:4000, size = n, replace = TRUE),
   v=runif(n = n, 0, 10000))
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 2000))
```
The results are showed above.

